---
title: "Most Common Physical Activities, Behavioral
  Risk Factor Surveillance System 2023"
subtitle: ''
author: Jasmine
date: "`r format(Sys.time(), '%B %d, %Y')`"
knit: (function(inputFile, encoding) { 
      rmarkdown::render(inputFile,
                        encoding=encoding, 
                        output_file="Output/Markdown.html") })
output:
  html_document:
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    theme: cosmo
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

# load packages
library(tidyverse)
library(here)
library(janitor)
library(survey)
library(srvyr)
library(flextable)
library(patchwork)
library(sjmisc)

# no scientific notation
options(scipen=999)
# NAs in tables as empty strings
options(knitr.kable.NA = "")

# check working directory
getwd()
here()
```

# Methods {.hidden .unlisted .unnumbered}

## Data wrangling

### Download data

Download data from 2023

-   [data](https://www.cdc.gov/brfss/annual_data/annual_2023.html)
-   [codebook](https://www.cdc.gov/brfss/annual_data/2023/zip/codebook23_llcp-v2-508.zip)

### Load data

```{r}
brfss23 <- rio::import(here("Input", "LLCP2023.XPT"))
save(brfss23, file = here("Input", "brfss23.Rdata"))

load(file = here("Input", "brfss23.Rdata"))

brfss23 %>% tabyl(`_RACE`) # check against codebook, n=313067 for _RACE=1
```

### Create new variables

#### Survey variables and sociodemographic characteristics

```{r}
df <- brfss23 %>% mutate(
  
  # create indicator for overall summary
  one = 1,
  
  # survey data variables
  # this syntax helps make the survey design object later
  strata = `_STSTR`,
  weight = `_LLCPWT`,
  
  # sex
  sex =  factor(x = SEXVAR,
                levels = c(2, 1),
                labels = c("Female", "Male"),
                ordered = FALSE),
  
  # age
  age = case_when(`_AGEG5YR` == 14 ~ NA, # missing
                  `_AGEG5YR` %in% c(1, 2) ~ 1, # 18–29 
                   `_AGEG5YR` %in% c(3, 4, 5) ~ 2, # 30–44
                  `_AGEG5YR` %in% c(6, 7) ~ 3, # 45–54
                  `_AGEG5YR` %in% c(8, 9) ~ 4, # 55–64
                  `_AGEG5YR` %in% c(10, 11) ~ 5, # 65–74
                  `_AGEG5YR` %in% c(12, 13) ~ 6, # ≥ 75 years
                  TRUE ~ NA),
  
  age = factor(x = age,
               levels = c(1, 2, 3, 4, 5, 6),
               labels = c("18–29", "30–44", "45–54", "55–64", "65–74", "≥75"),
               ordered = FALSE),
  
  # race/ethnicity
  raceeth = case_when(
    `_RACE` == 9 ~ NA,
    TRUE ~ `_RACE`),
  raceeth = factor(x = `_RACE`,
                levels = c(3, 4, 2, 8, 7, 5, 1, 6),
                labels = c("American Indian or Alaskan Native, non-Hispanic",
                           "Asian, non-Hispanic", 
                           "Black, non-Hispanic",
                           "Hispanic", 
                           "Multiracial, non-Hispanic",
                           "Native Hawaiian or other Pacific Islander, non-Hispanic",
                           "White, non-Hispanic", 
                           "Another single race, non-Hispanic"),
                ordered = FALSE),
  
  # education level
  edu = case_when(
    `_EDUCAG` == 9 ~ NA,
    TRUE ~ `_EDUCAG`),
  edu = factor(x = `_EDUCAG`,
               levels = c(1, 2, 3, 4),
               labels = c("Did not graduate high school",
                          "Graduated high school",
                          "Attended college or technical school",
                          "Graduated from college or technical school"),
               ordered = FALSE),
  
  # BMI
  bmi = factor(x = `_BMI5CAT`,
               levels = c(1, 2, 3, 4),
               labels = c("Underweight",
                          "Normal weight",
                          "Overweight",
                          "Obesity"),
               ordered = FALSE) 
  )
  
# check

# Return a list with factor levels and numeric codes for each factor column
lapply(df[ , sapply(df, is.factor)], function(v) {
  data.frame(Levels=levels(unique(sort(v))),
             Values=as.numeric(unique(sort(v))))
  })

# cross tabs between coded and original variables
df %>% tabyl(sex, SEXVAR)
df %>% dplyr::group_by(age, `_AGEG5YR`) %>% tally() %>% arrange(`_AGEG5YR`) %>% print(n = 20)
df %>% dplyr::group_by(raceeth, `_RACE`) %>% tally() %>% arrange(`_RACE`)
df %>% dplyr::group_by(edu, `_EDUCAG`) %>% tally() %>% arrange(`_EDUCAG`)
df %>% dplyr::group_by(bmi, `_BMI5CAT`) %>% tally() %>% arrange(`_BMI5CAT`)
```

#### Physical activities 
```{r}

# most common activities
## this code creates a new column for each activity, and participants can report up to two activities (so can have response of 1 for max of two columns)

df <- df %>% 
  mutate(
    walking = case_when(EXERANY2 == 2 ~ 0, # no PA in past month
                        EXERANY2 %in% c(7, 9, NA) ~ NA, # don't know or refused for PA in past month
                        EXERANY2 == 1 & (EXRACT12 == 1 | EXRACT22 == 1) ~ 1, 
                        TRUE ~ 0),
    running = case_when(EXERANY2 == 2 ~ 0, # no PA in past month
                        EXERANY2 %in% c(7, 9, NA) ~ NA, # don't know or refused for PA in past month
                        EXERANY2 == 1 & (EXRACT12 == 2 | EXRACT22 == 2) ~ 1, 
                        TRUE ~ 0),
    gardening = case_when(EXERANY2 == 2 ~ 0, # no PA in past month
                        EXERANY2 %in% c(7, 9, NA) ~ NA, # don't know or refused for PA in past month
                        EXERANY2 == 1 & (EXRACT12 == 3 | EXRACT22 == 3) ~ 1, 
                        TRUE ~ 0),
    bicycling = case_when(EXERANY2 == 2 ~ 0, # no PA in past month
                        EXERANY2 %in% c(7, 9, NA) ~ NA, # don't know or refused for PA in past month
                        EXERANY2 == 1 & (EXRACT12 == 4 | EXRACT22 == 4) ~ 1, 
                        TRUE ~ 0),
    aerobics = case_when(EXERANY2 == 2 ~ 0, # no PA in past month
                        EXERANY2 %in% c(7, 9, NA) ~ NA, # don't know or refused for PA in past month
                        EXERANY2 == 1 & (EXRACT12 == 5 | EXRACT22 == 5) ~ 1, 
                        TRUE ~ 0),
    calisthenics = case_when(EXERANY2 == 2 ~ 0, # no PA in past month
                        EXERANY2 %in% c(7, 9, NA) ~ NA, # don't know or refused for PA in past month
                        EXERANY2 == 1 & (EXRACT12 == 6 | EXRACT22 == 6) ~ 1, 
                        TRUE ~ 0),
    elliptical = case_when(EXERANY2 == 2 ~ 0, # no PA in past month
                        EXERANY2 %in% c(7, 9, NA) ~ NA, # don't know or refused for PA in past month
                        EXERANY2 == 1 & (EXRACT12 == 7 | EXRACT22 == 7) ~ 1, 
                        TRUE ~ 0),
    household = case_when(EXERANY2 == 2 ~ 0, # no PA in past month
                        EXERANY2 %in% c(7, 9, NA) ~ NA, # don't know or refused for PA in past month
                        EXERANY2 == 1 & (EXRACT12 == 8 | EXRACT22 == 8) ~ 1, 
                        TRUE ~ 0),
    weightlifting = case_when(EXERANY2 == 2 ~ 0, # no PA in past month
                        EXERANY2 %in% c(7, 9, NA) ~ NA, # don't know or refused for PA in past month
                        EXERANY2 == 1 & (EXRACT12 == 9 | EXRACT22 == 9) ~ 1, 
                        TRUE ~ 0),
    yoga = case_when(EXERANY2 == 2 ~ 0, # no PA in past month
                        EXERANY2 %in% c(7, 9, NA) ~ NA, # don't know or refused for PA in past month
                        EXERANY2 == 1 & (EXRACT12 == 10 | EXRACT22 == 10) ~ 1, 
                        TRUE ~ 0),
    other = case_when(EXERANY2 == 2 ~ 0, # no PA in past month
                        EXERANY2 %in% c(7, 9, NA) ~ NA, # don't know or refused for PA in past month
                        EXERANY2 == 1 & (EXRACT12 == 11 | EXRACT22 == 11) ~ 1, 
                        TRUE ~ 0)
    )

# check for walking
df %>%
  group_by(walking, EXERANY2, EXRACT12, EXRACT22) %>%
  summarise(Count = n(), .groups = 'drop') %>% 
  print(n=999)

```

#### Inclusion indicator
```{r}

# inclusion/exclusion
df <- df %>% 
  mutate(
    include = case_when(
      `_PA150R4` == 9 ~ FALSE, # missing aerobic data,
      is.na(sex) ~ FALSE, # missing sex data
      is.na(age) ~ FALSE, # missing age
      is.na(raceeth) ~ FALSE, # missing race/ethnicity 
      is.na(edu) ~ FALSE, # missing education
      is.na(bmi) ~ FALSE, # missing BMI
      .default = TRUE), # otherwise, include
    exclude = case_when(
      `_PA150R4` == 9 ~ "1. Missing aerobic PA data",
      is.na(sex) ~ "2. Missing sex",
      is.na(age) ~ "3. Missing age",
      is.na(raceeth) ~ "4. Missing race/ethnicity",
      is.na(edu) ~ "5. Missing education",
      is.na(bmi) ~ "6. Missing BMI",
      .default = "7. Include"))

# sample flow
df %>% tabyl(exclude, include)

# check variables for included vs excluded
df %>% group_by(include) %>% 
  skimr::skim(sex, age, raceeth, edu, bmi,
              `_PA150R4`,
              walking:other)
  
```

## Setup for weighted analyses

### Create survey design ojject using srvyr
```{r}
# https://wwwn.cdc.gov/nchs/data/Tutorials/Code/DB303_R.r
# https://www.cdc.gov/brfss/annual_data/2019/pdf/Complex-Smple-Weights-Prep-Module-Data-Analysis-2019-508.pdf

# Set options for allowing a single observation per stratum
options(survey.lonely.psu = "adjust")

# Create survey design using srvyr package 
brfssdsgn <- df %>%
  as_survey_design(ids = 1, # 1 for no cluster ids
                   weights = weight, # weight variable created above
                   strata = strata) # sampling was stratified

```

### Subset

```{r}

# Subsetting the original survey design object ensures we keep the design information about the number of clusters and strata
subset <- subset(brfssdsgn, include == 1)

# subset by sex
subset_female <- subset(brfssdsgn, include == 1 & sex == "Female")
subset_male <- subset(brfssdsgn, include == 1 & sex == "Male")
```

## Create functions

### Sample characteristics (only works on factors)

```{r}
# function for sample characteristics

sampleCharacteristics <- function(var,
                                  text = NULL,
                                  design = subset){

  # formulas
  formula_var = as.formula(paste("~", var))
  formula_one = as.formula("~ one")
  
  # row with header for characteristic
  header <- data.frame(characteristic = text)
  
    # get unweighted n
    n <- svyby(formula = formula_one, by = formula_var, design = design, 
               unwtd.count,
               na.rm.by = TRUE, na.rm.all = TRUE, na.rm = TRUE) %>% 
      rename(characteristic = var) %>% 
      select(characteristic, counts) %>% 
      `rownames<-`(NULL)  
    
    # get overall percentage/mean
    mean <- svyby(formula = formula_var, by = formula_one, design = design, 
                  svymean,
                  keep.var = TRUE, vartype = "se",
                  na.rm.by = TRUE, na.rm.all = TRUE, na.rm = TRUE) %>%
      select(starts_with(var)) %>% 
      pivot_longer(cols = everything(),
                   names_to = "characteristic",
                   values_to = "mean") %>%
      mutate(characteristic = case_when(
        # characteristic == "raceAnother single race, non-Hispanic" ~ "Another single race, non-Hispanic", # TODO check if we need this line
        characteristic == "employEmployed for wages or self-employed" ~ "Employed for wages or self-employed",
        TRUE ~ stringi::stri_replace_all_regex(characteristic, # remove suffixes for later merge
                                               pattern = var, 
                                               replacement='',
                                              vectorize=FALSE)))
     # get CI corresponding to overall percentage/mean 
     ci_l <- svyby(formula = formula_var, by = formula_one, design = design, 
                 svymean,
                 keep.var=TRUE, vartype="ci",
                 na.rm.by = TRUE, na.rm.all = TRUE, na.rm = TRUE) %>%
       select(starts_with("ci_l")) %>%
       pivot_longer(cols=c(starts_with("ci_l")),
                    names_to = "characteristic",
                    values_to = "ci_l") %>%
       mutate(characteristic = case_when(
         # characteristic == "ci_l.raceAnother single race, non-Hispanic" ~ "Another single race, non-Hispanic", # TODO check if we need this line
        characteristic == "ci_l.employEmployed for wages or self-employed" ~ "Employed for wages or self-employed",
         TRUE ~ stringi::stri_replace_all_regex(characteristic,
                                                pattern=c('ci_l\\.', var),
                                                replacement='',
                                                vectorize=FALSE)))
     
     ci_u <- svyby(formula = formula_var, by = formula_one, design = design, 
                 svymean,
                 keep.var=TRUE, vartype="ci",
                 na.rm.by = TRUE, na.rm.all = TRUE, na.rm = TRUE) %>%
       select(starts_with("ci_u")) %>%
       pivot_longer(cols=c(starts_with("ci_u")),
                    names_to = "characteristic",
                    values_to = "ci_u") %>%
       mutate(characteristic = case_when(
         # characteristic == "ci_u.raceAnother single race, non-Hispanic" ~ "Another single race, non-Hispanic", # TODO check if we need this line
        characteristic == "ci_u.employEmployed for wages or self-employed" ~ "Employed for wages or self-employed",
         TRUE ~ stringi::stri_replace_all_regex(characteristic,
                                                pattern=c('ci_u\\.', var),
                                                replacement='',
                                                vectorize=FALSE)))
    
    # combine n, mean, and CIs
     output <- bind_rows(header,
                         plyr::join_all(list(n, mean, ci_u, ci_l), by = "characteristic")) %>%
       mutate(
         suppress = case_when(
           counts < 30 ~ "1. small n",
           ci_u - ci_l > 0.05 &
             ((ci_u - ci_l) / mean > 1.3) ~ "2. wide absolute and relative CI width ",
           TRUE ~ "3. present data"
         ),
         display = case_when(
           # display estimate and 95% CI if not suppressed
           is.na(counts) ~ "", # make empty for header
           suppress != "3. present data" ~ "—",
           TRUE ~ paste0(formatC(mean * 100, digits = 1, format = "f"),
                                   " (", 
                                   formatC(ci_l * 100, digits = 1, format = "f"),
                                   "–", 
                         formatC(ci_u * 100, digits = 1, format = "f"), 
                                   ")")
         ))
     return(output)
}

```

### Prevelance of most common physical activities

```{r}
# function for prevalence and 95% CIs for most common activities

commonActivity <- function(varformula, byformula = ~one, design = subset, name){
  
  outcome <- as.character(varformula)[2]
  
  # Get mean, stderr, and unweighted sample size
  n <- svyby(~one, varformula, design, unwtd.count) %>% filter(.data[[outcome]]==1) %>% select(counts)
  p <- svyby(varformula, byformula, design, svymean, vartype = c("ci", "se"))
  
  outSum <- bind_cols(n, p) %>%  # combine
    mutate(suppress = # suppression flag
             case_when(
               counts < 50 ~ "1. small n",
               se/.data[[outcome]] > .3 ~ "2. large RSE",
               TRUE ~ "3. present data"),
           display = # estimate and 95% CI if not suppressed
             case_when(
               suppress !="3. present data" ~ "—",
               TRUE ~ paste0( # concatenate estimates and CIs
                 formatC(.data[[outcome]] * 100, digits = 1, format = "f"),
                 " (",
                 formatC(ci_l * 100, digits = 1, format = "f"),
                 "–",
                 formatC(ci_u * 100, digits = 1, format = "f"),
                 ")"))) %>% 
    rename(prev = .data[[outcome]]) %>%  # rename to be able to combine later
    mutate(activity = name) # new col with name of activity
  
  rownames(outSum) <- NULL # for index
  
  outSum
}
```

# Results

## Table 1. Sample characteristics

```{r}

# Table 1

# total for all
tbl1_total <- bind_rows(
  sampleCharacteristics(var = "sex", text = "Sex"),
  sampleCharacteristics(var = "age", text = "Age group (years)"),
  sampleCharacteristics(var = "raceeth", text = "Race/ethnicity"),
  sampleCharacteristics(var = "edu", text = "Level of education"),
  sampleCharacteristics(var = "bmi", text = "Body Mass Index")) %>% 
  select(characteristic, counts, display)

# females
tbl1_female <- bind_rows(
  sampleCharacteristics(var = "sex", text = "Sex", design = subset_female),
  sampleCharacteristics(var = "age", text = "Age group (years)", design = subset_female),
  sampleCharacteristics(var = "raceeth", text = "Race/ethnicity", design = subset_female),
  sampleCharacteristics(var = "edu", text = "Level of education", design = subset_female),
  sampleCharacteristics(var = "bmi", text = "Body Mass Index", design = subset_female)) %>% 
  select(characteristic, counts, display) %>% 
  rename(counts_female = counts,
         display_female = display)

# males
tbl1_male <- bind_rows(
  sampleCharacteristics(var = "sex", text = "Sex", design = subset_male),
  sampleCharacteristics(var = "age", text = "Age group (years)", design = subset_male),
  sampleCharacteristics(var = "raceeth", text = "Race/ethnicity", design = subset_male),
  sampleCharacteristics(var = "edu", text = "Level of education", design = subset_male),
  sampleCharacteristics(var = "bmi", text = "Body Mass Index", design = subset_male)) %>% 
  select(characteristic, counts, display) %>% 
  rename(counts_male = counts,
         display_male = display)

# join
tbl1 <- left_join(tbl1_total, tbl1_female,
                  by = "characteristic") %>% 
  left_join(tbl1_male, 
            by = "characteristic")

# table if not stratifying
tbl1_ft <- tbl1_total %>% 
  flextable() %>% 
  set_header_labels(
    characteristic = "Characteristic",
    counts = paste0("Unweighted n"),
    display = "Weighted % (95% CI)") %>%
  add_header_row(values = paste0("Table 1. Sample characteristics of US adults (N = ", df %>% filter(include == TRUE) %>% nrow() %>% sjmisc::big_mark(), "), Behavioral Risk Factor Surveillance System — United States, 2023"),
                 colwidths = tbl1_total %>% ncol()) %>% 
  italic(i = c(which(is.na(tbl1_total$counts))), # italics for readability
         j = 1) %>% 
  padding(i = c(which(!is.na(tbl1_total$counts))), # indent for readability
          j = 1,
          padding.left = 20) %>%
  padding(padding.top = 0, padding.bottom = 0) %>% 
  autofit(add_w=0) %>%
  flextable::fontsize(size = 10, part="all") %>%
  font(part="all", fontname = "Arial") %>% 
  set_table_properties(layout = "autofit") %>% 
  theme_vanilla()

# if stratifying by sex
tbl1_ft <- tbl1 %>% 
  flextable() %>% 
  set_header_labels(
    characteristic = "Characteristic",
    counts = "n",
    display = "% (95% CI)",
    counts_female = "n",
    display_female = "% (95% CI)",
    counts_male = "n",
    display_male = "% (95% CI)") %>%
  add_header_row(values = c("", "Total", "Females", "Males"),
                 colwidths = c(1, 2, 2, 2)) %>% 
  add_header_row(values = paste0("Table 1. Sample characteristics of US adults (N = ", df %>% filter(include == TRUE) %>% nrow() %>% sjmisc::big_mark(), "), Behavioral Risk Factor Surveillance System — United States, 2023"),
                 colwidths = tbl1 %>% ncol()) %>% 
  italic(i = c(which(is.na(tbl1$counts))), # italics for readability
         j = 1) %>% 
  padding(i = c(which(!is.na(tbl1$counts))), # indent for readability
          j = 1,
          padding.left = 20) %>%
  padding(padding.top = 0, padding.bottom = 0) %>% 
  flextable::footnote(i = 1,
                      j = 1,
                      part = "header",
                      value = as_paragraph(c("N's are unweighted. Prevalence %s and 95% CIs are weighted.")), 
                      ref_symbols = c("a")) %>%
  autofit(add_w=0) %>%
  flextable::fontsize(size = 10, part="all") %>%
  font(part="all", fontname = "Arial") %>% 
  set_table_properties(layout = "autofit") %>% 
  theme_vanilla()

# display
tbl1_ft

# TODO fix
```

## Table 2. Most common physical activities

```{r}

# total
tbl2_total <- bind_rows(
  commonActivity(varformula = ~walking, name = "Walking", design = subset),
  commonActivity(varformula = ~other, name = "Other", design = subset),
  commonActivity(varformula = ~running, name = "Running or jogging", design = subset),
  commonActivity(varformula = ~weightlifting, name = "Weight lifting", design = subset),
  commonActivity(varformula = ~household, name = "Household activities", design = subset),
  commonActivity(varformula = ~yoga, name = "Yoga, Pilates, or Tai Chi", design = subset),
  commonActivity(varformula = ~gardening, name = "Gardening or yard work", design = subset),
  commonActivity(varformula = ~bicycling, name = "Bicycling or bicyling machine exercise", design = subset),
  commonActivity(varformula = ~aerobics, name = "Aerobics video or class", design = subset),
  commonActivity(varformula = ~calisthenics, name = "Calisthenics", design = subset),
  commonActivity(varformula = ~elliptical, name = "Elliptical/EFX machine", design = subset)) %>% 
  arrange(desc(prev)) %>% 
  select(activity, counts, display)

# females
tbl2_female <- bind_rows(
  commonActivity(varformula = ~walking, name = "Walking", design = subset_female),
  commonActivity(varformula = ~other, name = "Other", design = subset_female),
  commonActivity(varformula = ~running, name = "Running or jogging", design = subset_female),
  commonActivity(varformula = ~weightlifting, name = "Weight lifting", design = subset_female),
  commonActivity(varformula = ~household, name = "Household activities", design = subset_female),
  commonActivity(varformula = ~yoga, name = "Yoga, Pilates, or Tai Chi", design = subset_female),
  commonActivity(varformula = ~gardening, name = "Gardening or yard work", design = subset_female),
  commonActivity(varformula = ~bicycling, name = "Bicycling or bicyling machine exercise", design = subset_female),
  commonActivity(varformula = ~aerobics, name = "Aerobics video or class", design = subset_female),
  commonActivity(varformula = ~calisthenics, name = "Calisthenics", design = subset_female),
  commonActivity(varformula = ~elliptical, name = "Elliptical/EFX machine", design = subset_female)) %>% 
  arrange(desc(prev)) %>% 
  rename(counts_female = counts,
         display_female = display) %>% 
  select(activity, counts_female, display_female)

# males
tbl2_male <- bind_rows(
  commonActivity(varformula = ~walking, name = "Walking", design = subset_male),
  commonActivity(varformula = ~other, name = "Other", design = subset_male),
  commonActivity(varformula = ~running, name = "Running or jogging", design = subset_male),
  commonActivity(varformula = ~weightlifting, name = "Weight lifting", design = subset_male),
  commonActivity(varformula = ~household, name = "Household activities", design = subset_male),
  commonActivity(varformula = ~yoga, name = "Yoga, Pilates, or Tai Chi", design = subset_male),
  commonActivity(varformula = ~gardening, name = "Gardening or yard work", design = subset_male),
  commonActivity(varformula = ~bicycling, name = "Bicycling or bicyling machine exercise", design = subset_male),
  commonActivity(varformula = ~aerobics, name = "Aerobics video or class", design = subset_male),
  commonActivity(varformula = ~calisthenics, name = "Calisthenics", design = subset_male),
  commonActivity(varformula = ~elliptical, name = "Elliptical/EFX machine", design = subset_male)) %>% 
  arrange(desc(prev)) %>% 
  rename(counts_male = counts,
         display_male = display) %>% 
  select(activity, counts_male, display_male)

# join
tbl2 <- left_join(tbl2_total, tbl2_female,
                  by = "activity") %>% 
  left_join(tbl2_male, 
            by = "activity")

# table if not stratifying by sex
tbl2_ft <- flextable(tbl2_total) %>% 
  autofit(add_w=0) %>% 
  add_header_row(values = as_paragraph("Table 2. Most common non-occupational physical activities among U.S. adults, Behavioral Risk Factor Surveillance System — United States, 2023"),
                 colwidths = 3) %>% 
  set_header_labels(activity = "Activity",
                    counts = "Unweighted n",
                    display = "Weighted % (95% confidence interval)") %>% 
  flextable::footnote(i = c(1, 1),
                      j = c(1, 1),
                      value = as_paragraph(c(
                        "Adults were included if they had complete data for aerobic activity.",
                        "If participants reported any past-month, non-occupational physical activity, they then described the type of their two most common activities.")),
                      part = "header",
                      ref_symbols = c("a", "b")) %>%
  flextable::fontsize(size = 9, part="all") %>%
  font(part="all", fontname = "Arial") %>% 
  set_table_properties(layout = "autofit") %>% 
  theme_vanilla()

# table if stratifying by sex
tbl2_ft <- tbl2 %>% 
  flextable() %>% 
  set_header_labels(
    activity = "Activity",
    counts = "n",
    display = "% (95% CI)",
    counts_female = "n",
    display_female = "% (95% CI)",
    counts_male = "n",
    display_male = "% (95% CI)") %>%
  add_header_row(values = c("", "Total", "Females", "Males"),
                 colwidths = c(1, 2, 2, 2)) %>% 
  add_header_row(values = paste0("Table 2. Most common non-occupational physical activities among U.S. adults (N = ", df %>% filter(include == TRUE) %>% nrow() %>% sjmisc::big_mark(), "), Behavioral Risk Factor Surveillance System — United States, 2023"),
                 colwidths = tbl2 %>% ncol()) %>% 
  flextable::footnote(i = c(1, 1, 1),
                      j = c(1, 1, 1),
                      value = as_paragraph(c(
                        "Adults were included if they had complete data for aerobic activity.",
                        "If participants reported any past-month, non-occupational physical activity, they then described the type of their two most common activities.",
                        "N's are unweighted. Prevalence %s and 95% CIs are weighted.")), 
                      part = "header",
                      ref_symbols = c("a", "b", "c")) %>%
  italic(i = c(which(is.na(tbl2$counts))), # italics for readability
         j = 1) %>% 
  padding(i = c(which(!is.na(tbl2$counts))), # indent for readability
          j = 1,
          padding.left = 20) %>%
  padding(padding.top = 0, padding.bottom = 0) %>% 
  autofit(add_w=0) %>%
  flextable::fontsize(size = 10, part="all") %>%
  font(part="all", fontname = "Arial") %>% 
  set_table_properties(layout = "autofit") %>% 
  theme_vanilla()

# display
tbl2_ft

```