---
title: "Most Common Physical Activities, Behavioral
  Risk Factor Surveillance System 2023"
subtitle: "Excludes people missing data for physical activities and sociodemographics"
author: Jasmine
date: "`r format(Sys.time(), '%B %d, %Y')`"
knit: (function(inputFile, encoding) { 
      rmarkdown::render(inputFile,
                        encoding=encoding, 
                        output_file="Output/Markdown.html") })
output:
  html_document:
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    theme: cosmo
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

# load packages
library(tidyverse)
library(here)
library(janitor)
library(survey)
library(srvyr)
library(flextable)
library(patchwork)
library(sjmisc)

# no scientific notation
options(scipen=999)
# NAs in tables as empty strings
options(knitr.kable.NA = "")

# check working directory
getwd()
here()
```

# Methods {.hidden .unlisted .unnumbered}

## Data wrangling

### Download data

Download data from 2023

-   [data](https://www.cdc.gov/brfss/annual_data/annual_2023.html)
-   [codebook](https://www.cdc.gov/brfss/annual_data/2023/zip/codebook23_llcp-v2-508.zip)

### Load data

```{r}
# brfss23 <- rio::import(here("Input", "LLCP2023.XPT"))
# save(brfss23, file = here("Input", "brfss23.Rdata"))

load(file = here("Input", "brfss23.Rdata"))

brfss23 %>% tabyl(`_RACE`) # check against codebook, n=313067 for _RACE=1
```

### Create new variables

#### Survey variables and sociodemographic characteristics

```{r}
df <- brfss23 %>% mutate(
  
  # create indicator for overall summary
  one = 1,
  
  # survey data variables
  # this syntax helps make the survey design object later
  strata = `_STSTR`,
  weight = `_LLCPWT`,
  
  # sex
  sex =  factor(x = SEXVAR,
                levels = c(2, 1),
                labels = c("Female", "Male"),
                ordered = FALSE),
  
  # age
  age = case_when(`_AGEG5YR` == 14 ~ NA, # missing
                  `_AGEG5YR` %in% c(1, 2) ~ 1, # 18–29 
                   `_AGEG5YR` %in% c(3, 4, 5) ~ 2, # 30–44
                  `_AGEG5YR` %in% c(6, 7) ~ 3, # 45–54
                  `_AGEG5YR` %in% c(8, 9) ~ 4, # 55–64
                  `_AGEG5YR` %in% c(10, 11) ~ 5, # 65–74
                  `_AGEG5YR` %in% c(12, 13) ~ 6, # ≥ 75 years
                  TRUE ~ NA),
  
  age = factor(x = age,
               levels = c(1, 2, 3, 4, 5, 6),
               labels = c("18–29", "30–44", "45–54", "55–64", "65–74", "≥75"),
               ordered = FALSE),
  
  # race/ethnicity
  raceeth = case_when(
    `_RACE` == 9 ~ NA,
    TRUE ~ `_RACE`),
  raceeth = factor(x = `_RACE`,
                levels = c(3, 4, 2, 8, 7, 5, 1, 6),
                labels = c("American Indian or Alaskan Native, non-Hispanic",
                           "Asian, non-Hispanic", 
                           "Black, non-Hispanic",
                           "Hispanic", 
                           "Multiracial, non-Hispanic",
                           "Native Hawaiian or other Pacific Islander, non-Hispanic",
                           "White, non-Hispanic", 
                           "Another single race, non-Hispanic"),
                ordered = FALSE),
  
  # education level
  edu = case_when(
    `_EDUCAG` == 9 ~ NA,
    TRUE ~ `_EDUCAG`),
  edu = factor(x = `_EDUCAG`,
               levels = c(1, 2, 3, 4),
               labels = c("Did not graduate high school",
                          "Graduated high school",
                          "Attended college or technical school",
                          "Graduated from college or technical school"),
               ordered = FALSE),
  
  # BMI
  bmi = factor(x = `_BMI5CAT`,
               levels = c(1, 2, 3, 4),
               labels = c("Underweight",
                          "Normal weight",
                          "Overweight",
                          "Obesity"),
               ordered = FALSE) 
  )
  
# check

# Return a list with factor levels and numeric codes for each factor column
lapply(df[ , sapply(df, is.factor)], function(v) {
  data.frame(Levels=levels(unique(sort(v))),
             Values=as.numeric(unique(sort(v))))
  })

# cross tabs between coded and original variables
df %>% tabyl(sex, SEXVAR)
df %>% dplyr::group_by(age, `_AGEG5YR`) %>% tally() %>% arrange(`_AGEG5YR`) %>% print(n = 20)
df %>% dplyr::group_by(raceeth, `_RACE`) %>% tally() %>% arrange(`_RACE`)
df %>% dplyr::group_by(edu, `_EDUCAG`) %>% tally() %>% arrange(`_EDUCAG`)
df %>% dplyr::group_by(bmi, `_BMI5CAT`) %>% tally() %>% arrange(`_BMI5CAT`)
```

#### Physical activities 
```{r}

# meeting aerobic PAG and most common activities
## this code creates a new column for each activity, and participants can report up to two activities (so can have response of 1 for max of two columns)

df <- df %>% 
  mutate(
    pag_aerobic = case_when(
      `_PA150R4` == 9 ~ NA, 
      TRUE ~ `_PA150R4`),
    pag_aerobic = factor(x = pag_aerobic,
               levels = c(1, 2, 3),
               labels = c("150+ minutes/week",
                          "1-149 minutes/week",
                          "0 minutes/week"),
               ordered = FALSE), 
    walking = case_when(EXERANY2 == 2 ~ 0, # no PA in past month
                        EXERANY2 %in% c(7, 9, NA) ~ NA, # don't know or refused for PA in past month
                        EXERANY2 == 1 & (EXRACT12 == 1 | EXRACT22 == 1) ~ 1, 
                        TRUE ~ 0),
    running = case_when(EXERANY2 == 2 ~ 0, # no PA in past month
                        EXERANY2 %in% c(7, 9, NA) ~ NA, # don't know or refused for PA in past month
                        EXERANY2 == 1 & (EXRACT12 == 2 | EXRACT22 == 2) ~ 1, 
                        TRUE ~ 0),
    gardening = case_when(EXERANY2 == 2 ~ 0, # no PA in past month
                        EXERANY2 %in% c(7, 9, NA) ~ NA, # don't know or refused for PA in past month
                        EXERANY2 == 1 & (EXRACT12 == 3 | EXRACT22 == 3) ~ 1, 
                        TRUE ~ 0),
    bicycling = case_when(EXERANY2 == 2 ~ 0, # no PA in past month
                        EXERANY2 %in% c(7, 9, NA) ~ NA, # don't know or refused for PA in past month
                        EXERANY2 == 1 & (EXRACT12 == 4 | EXRACT22 == 4) ~ 1, 
                        TRUE ~ 0),
    aerobics = case_when(EXERANY2 == 2 ~ 0, # no PA in past month
                        EXERANY2 %in% c(7, 9, NA) ~ NA, # don't know or refused for PA in past month
                        EXERANY2 == 1 & (EXRACT12 == 5 | EXRACT22 == 5) ~ 1, 
                        TRUE ~ 0),
    calisthenics = case_when(EXERANY2 == 2 ~ 0, # no PA in past month
                        EXERANY2 %in% c(7, 9, NA) ~ NA, # don't know or refused for PA in past month
                        EXERANY2 == 1 & (EXRACT12 == 6 | EXRACT22 == 6) ~ 1, 
                        TRUE ~ 0),
    elliptical = case_when(EXERANY2 == 2 ~ 0, # no PA in past month
                        EXERANY2 %in% c(7, 9, NA) ~ NA, # don't know or refused for PA in past month
                        EXERANY2 == 1 & (EXRACT12 == 7 | EXRACT22 == 7) ~ 1, 
                        TRUE ~ 0),
    household = case_when(EXERANY2 == 2 ~ 0, # no PA in past month
                        EXERANY2 %in% c(7, 9, NA) ~ NA, # don't know or refused for PA in past month
                        EXERANY2 == 1 & (EXRACT12 == 8 | EXRACT22 == 8) ~ 1, 
                        TRUE ~ 0),
    weightlifting = case_when(EXERANY2 == 2 ~ 0, # no PA in past month
                        EXERANY2 %in% c(7, 9, NA) ~ NA, # don't know or refused for PA in past month
                        EXERANY2 == 1 & (EXRACT12 == 9 | EXRACT22 == 9) ~ 1, 
                        TRUE ~ 0),
    yoga = case_when(EXERANY2 == 2 ~ 0, # no PA in past month
                        EXERANY2 %in% c(7, 9, NA) ~ NA, # don't know or refused for PA in past month
                        EXERANY2 == 1 & (EXRACT12 == 10 | EXRACT22 == 10) ~ 1, 
                        TRUE ~ 0),
    other = case_when(EXERANY2 == 2 ~ 0, # no PA in past month
                        EXERANY2 %in% c(7, 9, NA) ~ NA, # don't know or refused for PA in past month
                        EXERANY2 == 1 & (EXRACT12 == 11 | EXRACT22 == 11) ~ 1, 
                        TRUE ~ 0)
    )

# check for walking
df %>%
  group_by(walking, EXERANY2, EXRACT12, EXRACT22) %>%
  summarise(Count = n(), .groups = 'drop') %>% 
  print(n=999)

df %>% tabyl(`_PA150R4`, pag_aerobic)

```

#### Inclusion indicator
```{r}

# inclusion/exclusion
df <- df %>% 
  mutate( 
    # # if exclusion is based on aerobic data
    # include = case_when(
    #   `_PA150R4` == 9 ~ FALSE, # missing aerobic data,
    #   is.na(sex) ~ FALSE, # missing sex data
    #   is.na(age) ~ FALSE, # missing age
    #   is.na(raceeth) ~ FALSE, # missing race/ethnicity
    #   is.na(edu) ~ FALSE, # missing education
    #   is.na(bmi) ~ FALSE, # missing BMI
    #   .default = TRUE), # otherwise, include
    # exclude = case_when(
    #   `_PA150R4` == 9 ~ "1. Missing aerobic PA data",
    #   is.na(sex) ~ "2. Missing sex",
    #   is.na(age) ~ "3. Missing age",
    #   is.na(raceeth) ~ "4. Missing race/ethnicity",
    #   is.na(edu) ~ "5. Missing education",
    #   is.na(bmi) ~ "6. Missing BMI",
    #   .default = "7. Include"),
    
    # if exclusion is based on reported activities
    include = case_when( # TODO check this
      EXERANY2 %in% c(7, 9, NA) ~ FALSE, # don't know or refused for PA in past month
      EXERANY2 == 2 & complete.cases(sex, age, raceeth, edu, bmi) ~ TRUE, # include those with reported no past-month PA and have sociodemographic data
      EXERANY2 == 1 & (EXRACT12 %in% c(77, 99)) ~ FALSE, # yes for past-month PA, refused or don't know for first activity, they are all missing data for second activity
       !complete.cases(sex, age, raceeth, edu, bmi) ~ FALSE, # not complete cases for sociodemographic data
      .default = TRUE), # otherwise, include
    exclude = case_when( # TODO need to fix this to match the code above
      EXERANY2 %in% c(7, 9, NA) ~ "1. don't know, refused, missing for past-month PA", # don't know or refused for PA in past month
      !complete.cases(sex, age, raceeth, edu, bmi) ~ "2. missing sociodemographic data",
      # EXERANY2 != 2 & is.na(EXRACT12) & is.na(EXRACT22) ~ "3. missing data for both activities", # missing data for both activities, no one
      EXERANY2 == 1 & (EXRACT12 %in% c(77, 99)) ~ "3. refused for first activity, not asked about second", # refused or don't know for first activity, don't answer EXRACT22 #TODO check this one
      .default = "4. include") # otherwise, include
    ) 

# sample flow
df %>% tabyl(exclude, include)
df %>% tabyl(exclude)

# those with missing data for EXRACT12 also have missing for EXRACT22
df %>% filter(!(EXERANY2 %in% c(7, 9, NA) | (EXERANY2 == 2 & complete.cases(sex, age, raceeth, edu, bmi)))) %>% filter(is.na(EXRACT12)) %>% tabyl(EXRACT22)

# no respondent with NA for EXRACT12 if EXERANY==1
df %>% tabyl(EXERANY2, EXRACT12)

# all but 1 who have 77 or 99 for EXRACT12 are missing for EXRACT22. There is one with EXRACT12==1 and EXRACT22 is missing (who in included)
df %>% filter(EXERANY2==1) %>% tabyl(EXRACT12, EXRACT22)
df %>% filter(EXERANY2==1 & EXRACT12==1 & is.na(EXRACT22)) %>% select(include)
df %>% filter(EXERANY2==1) %>%  # yes past month PA
  filter(EXRACT12 %in% c(77, 99)) %>% # refused or don't know for first activity
  tabyl(EXRACT22) # all missing data for EXRACT22


# check variables for included vs excluded
df %>% group_by(include) %>% 
  skimr::skim(sex, age, raceeth, edu, bmi,
              `_PA150R4`, pag_aerobic,
              walking:other,
              EXERANY2, EXRACT12, EXRACT22)
  
```

## Setup for weighted analyses

### Create survey design ojject using srvyr
```{r}
# https://wwwn.cdc.gov/nchs/data/Tutorials/Code/DB303_R.r
# https://www.cdc.gov/brfss/annual_data/2019/pdf/Complex-Smple-Weights-Prep-Module-Data-Analysis-2019-508.pdf

# Set options for allowing a single observation per stratum
options(survey.lonely.psu = "adjust")

# Create survey design using srvyr package 
brfssdsgn <- df %>%
  as_survey_design(ids = 1, # 1 for no cluster ids
                   weights = weight, # weight variable created above
                   strata = strata) # sampling was stratified

```

### Subset

```{r}

# Subsetting the original survey design object ensures we keep the design information about the number of clusters and strata
subset <- subset(brfssdsgn, include == 1)

# subset by sex
subset_female <- subset(brfssdsgn, include == 1 & sex == "Female")
subset_male <- subset(brfssdsgn, include == 1 & sex == "Male")
```

## Create functions

### Function for Table 1 (overall prevalence for sample characteristics)

```{r}
# function for sample characteristics

overallPrevalence <- function(var,
                              text = NULL,
                              design){

  # formulas
  formula_var = as.formula(paste("~", var))
  formula_one = as.formula("~ one")
  

  
  # if variable is a factor
  if (design$variables[[var]] %>% is.factor()){
    
    # row with header for characteristic
    header <- data.frame(characteristic = text)
    
    # get unweighted n
    n <- svyby(formula = formula_one, by = formula_var, design = design, 
               unwtd.count,
               na.rm.by = TRUE, na.rm.all = TRUE, na.rm = TRUE) %>% 
      rename(characteristic = var) %>% 
      select(characteristic, counts) %>% 
      `rownames<-`(NULL)  
    
    # get overall percentage/mean
    mean <- svyby(formula = formula_var, by = formula_one, design = design, 
                  svymean,
                  keep.var = TRUE, vartype = "se",
                  na.rm.by = TRUE, na.rm.all = TRUE, na.rm = TRUE) %>%
      select(starts_with(var)) %>% 
      pivot_longer(cols = everything(),
                   names_to = "characteristic",
                   values_to = "mean") %>%
      mutate(characteristic = stringi::stri_replace_all_regex(characteristic, # remove suffixes for later merge
                                               pattern = var, 
                                               replacement='',
                                              vectorize=FALSE))
    
    # get SE
    se <- svyby(formula = formula_var, by = formula_one, design = design, 
                  svymean,
                  keep.var = TRUE, vartype = "se",
                  na.rm.by = TRUE, na.rm.all = TRUE, na.rm = TRUE) %>%
      select(starts_with("se.")) %>% 
      pivot_longer(cols = everything(),
                   names_to = "characteristic",
                   values_to = "se") %>%
      mutate(characteristic = stringi::stri_replace_all_regex(characteristic, # remove suffixes for later merge
                                               pattern = paste0("se.", var), 
                                               replacement='',
                                              vectorize=FALSE))
    
     # get CI corresponding to overall percentage/mean 
     ci_l <- svyby(formula = formula_var, by = formula_one, design = design, 
                 svymean,
                 keep.var=TRUE, vartype="ci",
                 na.rm.by = TRUE, na.rm.all = TRUE, na.rm = TRUE) %>%
       select(starts_with("ci_l")) %>%
       pivot_longer(cols=c(starts_with("ci_l")),
                    names_to = "characteristic",
                    values_to = "ci_l") %>%
       mutate(characteristic = stringi::stri_replace_all_regex(characteristic,
                                                pattern=c('ci_l\\.', var),
                                                replacement='',
                                                vectorize=FALSE))
     
     ci_u <- svyby(formula = formula_var, by = formula_one, design = design, 
                 svymean,
                 keep.var=TRUE, vartype="ci",
                 na.rm.by = TRUE, na.rm.all = TRUE, na.rm = TRUE) %>%
       select(starts_with("ci_u")) %>%
       pivot_longer(cols=c(starts_with("ci_u")),
                    names_to = "characteristic",
                    values_to = "ci_u") %>%
       mutate(characteristic = stringi::stri_replace_all_regex(characteristic,
                                                pattern=c('ci_u\\.', var),
                                                replacement='',
                                                vectorize=FALSE))
    
    # combine n, mean, and CIs
     output <- bind_rows(header,
                         plyr::join_all(list(n, mean, se, ci_u, ci_l), by = "characteristic")) %>%
       mutate(
         # https://www.cdc.gov/brfss/annual_data/2023/pdf/Compare_2023-508.pdf
         suppress = case_when(
           counts < 50 ~ "1. small n",
           se/mean > 0.3 ~ "2. wide RSE",
           TRUE ~ "3. present data"
         ),
         display = case_when(
           # display estimate and 95% CI if not suppressed
           is.na(counts) ~ "", # make empty for header
           suppress != "3. present data" ~ "—",
           TRUE ~ paste0(formatC(mean * 100, digits = 1, format = "f"),
                                   " (", 
                                   formatC(ci_l * 100, digits = 1, format = "f"),
                                   "–", 
                         formatC(ci_u * 100, digits = 1, format = "f"), 
                                   ")")
         ))
  
  # if variable is logical
     } else if (design$variables[[var]] %>% is.numeric()){
       
       # unweighted n for numerator
       n <- svyby(formula = formula_one, 
                  by = formula_var, 
                  design = design,
                  unwtd.count,
                  na.rm.by = TRUE, na.rm.all = TRUE, na.rm = TRUE) %>% 
         filter(.data[[var]]==1) %>% 
         select(counts)
       
       # weighted
       mean <- svyby(formula = formula_var,
                     by = formula_one,
                     design = design, 
                     svymean, 
                     vartype = c("ci", "se")) %>% 
         select(-one)
       
       output <- bind_cols(n, mean) %>%  # combine
         mutate(suppress = # suppression flag
                  case_when(
                    counts < 50 ~ "1. small n",
                    se/.data[[var]] > .3 ~ "2. large RSE",
                    TRUE ~ "3. present data"),
                display = # estimate and 95% CI if not suppressed
                  case_when(
                    suppress !="3. present data" ~ "—",
                    TRUE ~ paste0( # concatenate estimates and CIs
                      formatC(.data[[var]] * 100, digits = 1, format = "f"),
                      " (",
                      formatC(ci_l * 100, digits = 1, format = "f"),
                      "–",
                      formatC(ci_u * 100, digits = 1, format = "f"),
                      ")"))) %>%
         rename(mean = .data[[var]]) %>%  # rename to be able to combine later
         mutate(characteristic = text) %>% # new col with name of activity
         `rownames<-`(NULL) # remove named index
       }

  return(output)
}

```

<!-- ### Prevalence of most common physical activities -->

<!-- ```{r} -->
<!-- # function for prevalence and 95% CIs for most common activities -->

<!-- commonActivity <- function(varformula, byformula = ~one, design, name){ -->

<!--   outcome <- as.character(varformula)[2] -->

<!--   # Get mean, stderr, and unweighted sample size -->
<!--   n <- svyby(~one, varformula, design, unwtd.count) %>% filter(.data[[outcome]]==1) %>% select(counts) -->
<!--   p <- svyby(varformula, byformula, design, svymean, vartype = c("ci", "se")) -->

<!--   outSum <- bind_cols(n, p) %>%  # combine -->
<!--     mutate(suppress = # suppression flag -->
<!--              case_when( -->
<!--                counts < 50 ~ "1. small n", -->
<!--                se/.data[[outcome]] > .3 ~ "2. large RSE", -->
<!--                TRUE ~ "3. present data"), -->
<!--            display = # estimate and 95% CI if not suppressed -->
<!--              case_when( -->
<!--                suppress !="3. present data" ~ "—", -->
<!--                TRUE ~ paste0( # concatenate estimates and CIs -->
<!--                  formatC(.data[[outcome]] * 100, digits = 1, format = "f"), -->
<!--                  " (", -->
<!--                  formatC(ci_l * 100, digits = 1, format = "f"), -->
<!--                  "–", -->
<!--                  formatC(ci_u * 100, digits = 1, format = "f"), -->
<!--                  ")"))) %>%  -->
<!--     rename(prev = .data[[outcome]]) %>%  # rename to be able to combine later -->
<!--     mutate(activity = name) # new col with name of activity -->

<!--   rownames(outSum) <- NULL # for index -->

<!--   outSum -->
<!-- } -->
<!-- ``` -->

### Function for Tables 2 and 3 (stratified estimates for physical activities)

```{r}
# function to get unweighted n, weighted prevalence mean (95% CI), weighted chi-sq for categorical

stratifiedPrevalence <- function(outcome, var, text = NA, design) {
  # formulas
  formula_var = as.formula(paste("~", var))
  formula_outcome = as.formula(paste("~", outcome))
  mean_text <- paste0(outcome, "TRUE")
  ci_low <- paste0("ci_l.", outcome, "TRUE")
  ci_up <- paste0("ci_u.", outcome, "TRUE")
  
  # unweighted n
  n <- svyby(
    formula = formula_outcome,
    by = formula_var,
    design = design,
    unwtd.count,
    na.rm.by = TRUE,
    na.rm.all = TRUE,
    na.rm = TRUE
  ) %>%
    rename(characteristic = var) %>%
    select(characteristic, counts) %>%
    `rownames<-`(NULL)
  
  # weighted mean and CI
  ci <- svyby(
    formula = formula_outcome,
    by = formula_var,
    design = design,
    svymean,
    vartype = "ci",
    na.rm.by = TRUE,
    na.rm.all = TRUE,
    na.rm = TRUE
  ) %>%
    rename(characteristic = var,
           mean = outcome) %>%
    `rownames<-`(NULL) %>% 
    select(characteristic, mean, ci_l, ci_u)
  
  # weighted SE for mean
  se <- svyby(formula = formula_outcome, by = formula_var, design = design, 
                  svymean,
                  keep.var = TRUE, vartype = "se",
                  na.rm.by = TRUE, na.rm.all = TRUE, na.rm = TRUE) %>% 
    rename(characteristic = var) %>% 
    select(characteristic, se) %>% 
    `rownames<-`(NULL) 

  # # for overall estimates
  # if (var == "one"){
  #   output <- left_join(n, ci) %>% 
  #     mutate(characteristic = text,
  #            pvalue = NA,
  #            suppress = case_when( # suppression flag
  #              counts < 50 ~ "1. small n",
  #              ci_u - ci_l > 0.05 &
  #                ((ci_u - ci_l) / mean > 1.3) ~ "2. wide absolute and relative CI width ", # TODO change to SE
  #              TRUE ~ "3. present data"), 
  #            prev = case_when( # display estimate and 95% CI if not suppressed
  #              suppress != "3. present data" ~ "—",
  #              is.na(mean) ~ "",
  #              TRUE ~ paste0(
  #                # concatenate estimates and CIs
  #                formatC(mean * 100, digits = 1, format = "f"),
  #                " (",
  #                formatC(ci_l * 100, digits = 1, format = "f"),
  #                "–",
  #                formatC(ci_u * 100, digits = 1, format = "f"),
  #                ")"
  #              )
  #            )
  #     )
  #   # for subgroup estimates, get weighted p-value for chi-sq test
  # } else {
    output <- bind_rows(
    data.frame(
      characteristic = text,
      p.value = svychisq(as.formula(paste0("~", outcome, "+", var)), design, statistic =
                      "adjWald")$p.value %>% as.numeric()),
    plyr::join_all(list(n, ci, se), by = "characteristic")) %>%
    mutate(
      pvalue = case_when(
        p.value >= 0.001 ~ formatC(p.value, digits = 3, format = "f"), #3 decimals for p-value
        p.value < 0.001 ~ "<0.001",
        TRUE ~ ""
      ),
      suppress = # suppression flag
        case_when(
          counts < 30 ~ "1. small n",
          se/mean > 0.3 ~ "2. wide RSE",
          TRUE ~ "3. present data"
        ),
      prev = # present estimate and 95% CI if not suppressed
        case_when(
          suppress != "3. present data" ~ "—",
          is.na(mean) ~ "",
          TRUE ~ paste0(
            # concatenate estimates and CIs
            formatC(mean * 100, digits = 1, format = "f"),
            " (",
            formatC(ci_l * 100, digits = 1, format = "f"),
            "–",
            formatC(ci_u * 100, digits = 1, format = "f"),
            ")")
        ),
      display = # column with either pvalue or prevalence
        case_when(
          pvalue != "" ~ pvalue, 
          prev != "" ~ prev,
          TRUE ~ "")
    )
    # }
  
  return(output)
}
```

# Results

## Sample flow
```{r}
df %>% tabyl(exclude) %>% 
  mutate(percent = percent * 100) %>% 
  flextable() %>% 
  set_header_labels(
    exclude = "Criteria",
    percent = "%")
```


## Table 1. Sample characteristics

```{r}

# Table 1

# total for all
tbl1_total <- bind_rows(
  bind_rows(
    overallPrevalence(var = "age", text = "Age group (years)", design = subset),
    overallPrevalence(var = "raceeth", text = "Race and ethnicity", design = subset),
    overallPrevalence(var = "edu", text = "Level of education", design = subset),
    overallPrevalence(var = "bmi", text = "Body Mass Index category", design = subset),
        # overallPrevalence(var = "pag_aerobic", text = "Participation in aerobic physical activity", design = subset),
    data.frame(characteristic = "Physical Activity")) %>% 
    select(characteristic, counts, display),
  bind_rows(
    overallPrevalence(var = "walking", text = "Walking", design = subset),
    overallPrevalence(var = "other", text = "Other", design = subset),
    overallPrevalence(var = "running", text = "Running or jogging", design = subset),
    overallPrevalence(var = "weightlifting", text = "Weight lifting", design = subset),
    overallPrevalence(var = "household", text = "Household activities", design = subset),
    overallPrevalence(var = "yoga", text = "Yoga, Pilates, or Tai Chi", design = subset),
    overallPrevalence(var = "gardening", text = "Gardening or yard work", design = subset),
    overallPrevalence(var = "bicycling", text = "Bicycling or bicycling machine exercise", design = subset),
    overallPrevalence(var = "aerobics", text = "Aerobics video or class", design = subset),
    overallPrevalence(var = "calisthenics", text = "Calisthenics", design = subset),
    overallPrevalence(var = "elliptical", text = "Elliptical/EFX machine", design = subset)) %>%
    arrange(desc(mean)) %>%
    select(characteristic, counts, display))


# females
tbl1_female <- bind_rows(
  bind_rows(
    overallPrevalence(var = "age", text = "Age group (years)", design = subset_female),
    overallPrevalence(var = "raceeth", text = "Race/ethnicity", design = subset_female),
    overallPrevalence(var = "edu", text = "Level of education", design = subset_female),
    overallPrevalence(var = "bmi", text = "Body Mass Index", design = subset_female),
        overallPrevalence(var = "pag_aerobic", text = "Participation in aerobic physical activity", design = subset_female),
    data.frame(characteristic = "Physical Activity")) %>% 
    select(characteristic, counts, display),
  bind_rows(
    overallPrevalence(var = "walking", text = "Walking", design = subset_female),
    overallPrevalence(var = "other", text = "Other", design = subset_female),
    overallPrevalence(var = "running", text = "Running or jogging", design = subset_female),
    overallPrevalence(var = "weightlifting", text = "Weight lifting", design = subset_female),
    overallPrevalence(var = "household", text = "Household activities", design = subset_female),
    overallPrevalence(var = "yoga", text = "Yoga, Pilates, or Tai Chi", design = subset_female),
    overallPrevalence(var = "gardening", text = "Gardening or yard work", design = subset_female),
    overallPrevalence(var = "bicycling", text = "Bicycling or bicycling machine exercise", design = subset_female),
    overallPrevalence(var = "aerobics", text = "Aerobics video or class", design = subset_female),
    overallPrevalence(var = "calisthenics", text = "Calisthenics", design = subset_female),
    overallPrevalence(var = "elliptical", text = "Elliptical/EFX machine", design = subset_female)) %>%
    arrange(desc(mean)) %>%
    select(characteristic, counts, display)) %>% 
  rename(counts_female = counts,
         display_female = display)

# males
tbl1_male <- bind_rows(
  bind_rows(
    overallPrevalence(var = "age", text = "Age group (years)", design = subset_male),
    overallPrevalence(var = "raceeth", text = "Race/ethnicity", design = subset_male),
    overallPrevalence(var = "edu", text = "Level of education", design = subset_male),
    overallPrevalence(var = "bmi", text = "Body Mass Index", design = subset_male),
        overallPrevalence(var = "pag_aerobic", text = "Participation in aerobic physical activity", design = subset_male),
    data.frame(characteristic = "Physical Activity")) %>% 
    select(characteristic, counts, display),
  bind_rows(
    overallPrevalence(var = "walking", text = "Walking", design = subset_male),
    overallPrevalence(var = "other", text = "Other", design = subset_male),
    overallPrevalence(var = "running", text = "Running or jogging", design = subset_male),
    overallPrevalence(var = "weightlifting", text = "Weight lifting", design = subset_male),
    overallPrevalence(var = "household", text = "Household activities", design = subset_male),
    overallPrevalence(var = "yoga", text = "Yoga, Pilates, or Tai Chi", design = subset_male),
    overallPrevalence(var = "gardening", text = "Gardening or yard work", design = subset_male),
    overallPrevalence(var = "bicycling", text = "Bicycling or bicycling machine exercise", design = subset_male),
    overallPrevalence(var = "aerobics", text = "Aerobics video or class", design = subset_male),
    overallPrevalence(var = "calisthenics", text = "Calisthenics", design = subset_male),
    overallPrevalence(var = "elliptical", text = "Elliptical/EFX machine", design = subset_male)) %>%
    arrange(desc(mean)) %>%
    select(characteristic, counts, display)) %>% 
  rename(counts_male = counts,
         display_male = display)

# join
tbl1 <- left_join(tbl1_total, tbl1_female,
                  by = "characteristic") %>% 
  left_join(tbl1_male, 
            by = "characteristic")

# # table if not stratifying
# tbl1_ft <- tbl1_total %>% 
#   flextable() %>% 
#   set_header_labels(
#     characteristic = "Characteristic",
#     counts = paste0("Unweighted n"),
#     display = "Weighted % (95% CI)") %>%
#   add_header_row(values = paste0("Table 1. Sample characteristics of US adults (N = ", df %>% filter(include == TRUE) %>% nrow() %>% sjmisc::big_mark(), "), Behavioral Risk Factor Surveillance System — United States, 2023"),
#                  colwidths = tbl1_total %>% ncol()) %>% 
#   italic(i = c(which(is.na(tbl1_total$counts))), # italics for readability
#          j = 1) %>% 
#   padding(i = c(which(!is.na(tbl1_total$counts))), # indent for readability
#           j = 1,
#           padding.left = 20) %>%
#   padding(padding.top = 0, padding.bottom = 0) %>% 
#   autofit(add_w=0) %>%
#   flextable::fontsize(size = 10, part="all") %>%
#   font(part="all", fontname = "Arial") %>% 
#   set_table_properties(layout = "autofit") %>% 
#   theme_vanilla()

# if stratifying by sex
tbl1_ft <- tbl1 %>% 
  flextable() %>% 
  set_header_labels(
    characteristic = "Characteristic",
    counts = "n",
    display = "% (95% CI)",
    counts_female = "n",
    display_female = "% (95% CI)",
    counts_male = "n",
    display_male = "% (95% CI)") %>%
  add_header_row(values = c("", 
                            paste0("Total (n = ", df %>% filter(include == TRUE) %>% nrow() %>% sjmisc::big_mark(), ")"),  
                            paste0("Females (n = ", df %>% filter(include == TRUE & sex == "Female") %>% nrow() %>% sjmisc::big_mark(), ")"), 
                            paste0("Males (n = ", df %>% filter(include == TRUE & sex == "Male") %>% nrow() %>% sjmisc::big_mark(), ")")), 
                 colwidths = c(1, 2, 2, 2)) %>% 
  add_header_row(values = paste0("Table 1. Sample characteristics of US adults, Behavioral Risk Factor Surveillance System — United States, 2023"),
                 colwidths = tbl1 %>% ncol()) %>% 
  italic(i = c(which(is.na(tbl1$counts))), # italics for readability
         j = 1) %>% 
  padding(i = c(which(!is.na(tbl1$counts))), # indent for readability
          j = 1,
          padding.left = 20) %>%
  padding(padding.top = 0, padding.bottom = 0) %>% 
  flextable::footnote(i = 1,
                      j = 1,
                      part = "header",
                      value = as_paragraph(c("N's are unweighted. Prevalence %s and 95% CIs are weighted.")), 
                      ref_symbols = c("a")) %>%
  autofit(add_w=0) %>%
  flextable::fontsize(size = 10, part="all") %>%
  font(part="all", fontname = "Arial") %>% 
  set_table_properties(layout = "autofit") %>% 
  theme_vanilla()

# display
tbl1_ft
```

## Table 2. Females' most common physical activities

```{r}
# outcomes for both Table 2 and 3
outcomes <- c("walking",
              "other",
              "weightlifting",
              "gardening",
              "running",
              "bicycling",
              "household",
              "yoga",
              "calisthenics",
              "aerobics",
              "elliptical")

outcomes_female <- c("walking",
              "gardening",
              "weightlifting",
              "running",
              "household")

outcomes_male <- c("walking",
              "weightlifting",
              "running",
              "gardening",
              "bicycling")
```

```{r}
# FEMALES

# Initialize an empty data frame
tbl2 <- data.frame(
  characteristic = character(),
  stringsAsFactors = FALSE
)

# Loop through each outcome and create the corresponding data frame
for (i in outcomes_female) {
  temp_tbl2 <- bind_rows(
    stratifiedPrevalence(outcome = i, var = "age", text = "Age group (years)", design = subset_female),
    stratifiedPrevalence(outcome = i, var = "raceeth", text = "Race and ethnicity", design = subset_female),
    stratifiedPrevalence(outcome = i, var = "edu", text = "Education level", design = subset_female),
    stratifiedPrevalence(outcome = i, var = "bmi", text = "Body Mass Index category", design = subset_female)
    ) %>%
    select(characteristic, display) %>% # TODO add pvalue column?
    rename(!!i := display) # Use !! to dynamically name the column
  
  # Merge the temporary table into the main data frame
  tbl2 <- full_join(tbl2, temp_tbl2, by = "characteristic")
}

rm(i, temp_tbl2)

# make flextable
tbl2_ft <- flextable(tbl2) %>% 
  autofit(add_w=0) %>%
  add_header_row(values = c("", "Chi-square p-value or prevalence of physical activity, % (95% CI)"),
                 colwidths = c(1, tbl2 %>% ncol() - 1)) %>%
  add_header_row(values = as_paragraph("Table 2. Females' five most common non-occupational physical activities, Behavioral Risk Factor Surveillance System — United States, 2023"),
                 colwidths = tbl2 %>% ncol()) %>% 
  set_header_labels(characteristic = "Characteristic",
                    walking = "Walking",
                    other = "Other",
                    weightlifting = "Weight lifting",
                    household = "Household activities",
                    yoga = "Yoga, Pilates, or Tai Chi",
                    gardening = "Gardening or yard work",
                    running = "Running or jogging",
                    bicycling = "Bicycling or bicycling machine exercise",
                    aerobics = "Aerobics video or class",
                    calisthenics = "Calisthenics",
                    elliptical = "Elliptical/EFX machine") %>% 
  flextable::footnote(i = c(1, 1),
                      j = c(1, 1),
                      value = as_paragraph(c(
                        "Adults were included if they had complete data for aerobic activity.",
                        "If participants reported any past-month, non-occupational physical activity, they then described the type of their two most common activities.")),
                      part = "header",
                      ref_symbols = c("a", "b")) %>%
  flextable::footnote(i = which(tbl2 == "—", arr.ind = TRUE)[, 1], 
                      j = which(tbl2 == "—", arr.ind = TRUE)[, 2],
                      part = "body",
                      value = as_paragraph(c(
                        "This estimate is not presented because it has a relative standard error >30%.")),
                      ref_symbols = c("c")) %>% 
  italic(i = which(!grepl("–", tbl2$walking)), # italics
         j = NULL) %>%
  padding(i = which(grepl("–", tbl2$walking)), # indent
          j = 1,
          padding.left = 20) %>%
  padding(padding.top = 0, padding.bottom = 0) %>% 
  autofit(add_w = 0) %>%
  flextable::fontsize(size = 10, part = "all") %>%
  font(part = "all", fontname = "Arial") %>% 
  set_table_properties(layout = "autofit") %>% 
  theme_vanilla()

tbl2_ft
```

## Table 3. Males' most common physical activities

```{r}

# MALES

# Initialize an empty data frame
tbl3 <- data.frame(
  characteristic = character(),
  stringsAsFactors = FALSE
)

# Loop through each outcome and create the corresponding data frame
for (i in outcomes_male) {
  temp_tbl3 <- bind_rows(
    stratifiedPrevalence(outcome = i, var = "age", text = "Age group (years)", design = subset_male),
    stratifiedPrevalence(outcome = i, var = "raceeth", text = "Race and ethnicity", design = subset_male),
    stratifiedPrevalence(outcome = i, var = "edu", text = "Education level", design = subset_male),
    stratifiedPrevalence(outcome = i, var = "bmi", text = "Body Mass Index category", design = subset_male)
    ) %>%
    select(characteristic, display) %>% # TODO add pvalue column by changing prev to display?
    rename(!!i := display) # Use !! to dynamically name the column
  
  # Merge the temporary table into the main data frame
  tbl3 <- full_join(tbl3, temp_tbl3, by = "characteristic")
}

rm(i, temp_tbl3)

# make flextable
tbl3_ft <- flextable(tbl3) %>% 
  autofit(add_w=0) %>%
  add_header_row(values = c("", "Prevalence of physical activity, % (95% CI)"),
                 colwidths = c(1, tbl3 %>% ncol() - 1)) %>%
  add_header_row(values = as_paragraph("Table 3. Males' five most common non-occupational physical activities, Behavioral Risk Factor Surveillance System — United States, 2023"),
                 colwidths = tbl3 %>% ncol()) %>% 
  set_header_labels(characteristic = "Characteristic",
                    walking = "Walking",
                    other = "Other",
                    weightlifting = "Weight lifting",
                    household = "Household activities",
                    yoga = "Yoga, Pilates, or Tai Chi",
                    gardening = "Gardening or yard work",
                    running = "Running or jogging",
                    bicycling = "Bicycling or bicycling machine exercise",
                    aerobics = "Aerobics video or class",
                    calisthenics = "Calisthenics",
                    elliptical = "Elliptical/EFX machine") %>% 
  flextable::footnote(i = c(1, 1),
                      j = c(1, 1),
                      value = as_paragraph(c(
                        "Adults were included if they had complete data for aerobic activity.",
                        "If participants reported any past-month, non-occupational physical activity, they then described the type of their two most common activities.")),
                      part = "header",
                      ref_symbols = c("a", "b")) %>%
  flextable::footnote(i = which(tbl3 == "—", arr.ind = TRUE)[, 1], 
                      j = which(tbl3 == "—", arr.ind = TRUE)[, 2],
                      part = "body",
                      value = as_paragraph(c(
                        "This estimate is not presented because it has a relative standard error >30%.")),
                      ref_symbols = c("c")) %>% 
  italic(i = which(!grepl("–", tbl3$walking)), # italics
         j = NULL) %>%
  padding(i = which(grepl("–", tbl3$walking)), # indent
          j = 1,
          padding.left = 20) %>%
  padding(padding.top = 0, padding.bottom = 0) %>% 
  autofit(add_w = 0) %>%
  flextable::fontsize(size = 10, part = "all") %>%
  font(part = "all", fontname = "Arial") %>% 
  set_table_properties(layout = "autofit") %>% 
  theme_vanilla()

tbl3_ft
```
